---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cbrCurrency

<!-- badges: start -->
<!-- badges: end -->

The cbrCurrency package provides few functions for working with currency rates (currency to RUB as 1-to-1) from Central Bank of Russia. Most useful function is `cbr_mutate_rates()`.

## Installation

You can install cbrCurrency package from [GitHub](https://github.com/krasovskyd/cbrCurrency) with:

``` r
remotes::install_github('krasovskyd/cbrCurrency')
```

## Example

This is a basic example which shows you how to mutate column with different currencies and date rates (use `handleNA = TRUE` if exchange rate on required date not available)

```{r example}
library(magrittr)
library(cbrCurrency)

# some toy data
currency_df <- data.frame(stringsAsFactors = FALSE,

    date = sample(seq(as.Date('2017/04/01'),
                      as.Date('2020/01/01'), by="day"), 
                  150),

    currency = sample(c('USD', 'GBP', 'JPY', 'EUR', 'HKD',
                        'CNY', 'CHF', 'CAD'),
                      150,
                      replace = TRUE)
) %>% 
  tibble::as_tibble() %>% 
  dplyr::mutate(n = 1:nrow(.)) %>% 
  dplyr::relocate('n')

currency_df <- cbr_mutate_rates(currency_df, handleNA = TRUE)
currency_df
```

## Issues

If you find bug please force this in Issues or sent feedback on <krasovsky.d.a@gmail.com>
